GROUP NAME: We R
COURSE: DSC 423
TOPIC: COVID-19 CASES & DEATHS WORLDWIDE
PROJECT REPORT CODE:
---
title: "COVID-19 CASES & DEATHS WORLDWIDE ANALYSIS"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Descriptive statistics:

```{r cars}
# Load the dataset
    
# Summary statistics of cases and deaths
summary(covid_data[c("Total.Cases", "Total.Deaths")])

# Distribution of cases and deaths across different countries
by_country <- aggregate(covid_data[c("Total.Cases", "Total.Deaths")], by=list(covid_data$Country), FUN=sum)
barplot(height=by_country$Total.Cases, names.arg=by_country$Group.1, xlab="Country", ylab="Total Cases", main="Total Cases by Country")
barplot(height=by_country$Total.Deaths, names.arg=by_country$Group.1, xlab="Country", ylab="Total Deaths", main="Total Deaths by Country")
```

## Hypothesis testing:

```{r pressure, echo=FALSE}
# Load the dataset

# Test for significant difference in the number of cases and deaths between different countries
# Using t-test for independent samples
usa_cases <- covid_data$Total.Cases[covid_data$Country=="USA"]
india_cases <- covid_data$Total.Cases[covid_data$Country=="India"]
t.test(usa_cases, india_cases)

usa_deaths <- covid_data$Total.Deaths[covid_data$Country=="USA"]
india_deaths <- covid_data$Total.Deaths[covid_data$Country=="India"]
t.test(usa_deaths, india_deaths)
```


##Correlation analysis:

```{r pressure, echo=FALSE}
# Load the dataset

# Correlation between number of cases and deaths in different countries
cor(covid_data[c("Total.Cases", "Total.Deaths")])

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Simple linear regression:

```{r pressure, echo=FALSE}
# Load the dataset

# Model relationship between cases and deaths in a single country (e.g. USA)
usa_data <- covid_data[covid_data$Country=="USA", c("Total.Cases", "Total.Deaths")]
model <- lm(Total.Deaths ~ Total.Cases, data=usa_data)
summary(model)


```

##Multiple linear regression:

```{r pressure, echo=FALSE}
# Load the dataset

# Model relationship between cases and deaths in multiple countries
model <- lm(Total.Deaths ~ Total.Cases + Country, data=covid_data)
summary(model)



```
